---
title: "Drone Fight Analysis"
output:
  html_document:
    df_print: paged
---

```{r loadData, echo=FALSE, warning=FALSE, message=FALSE}
knitr::opts_chunk$set(echo = FALSE, comment = "", warning = FALSE, message = FALSE)
library(readr)
library(chron)
library(hms)
library(lubridate)
library(dplyr)
library(shiny)
library(data.table)
library(DT)
library(readxl)
library(ggplot2)
source("DroneTaggingFilterFunctions.r")
result <- readRDS("result.rds")
weather <- readRDS("data/weather.rds")
```
Observations
```{r observationData}
print(paste("# of observations:", result$nObs))
print(paste("# of drones (tags):", result$nTags))
print(paste("# of 'orphan' observations (a single observation for one drone on a day:", result$nOneObs))
print("# of observations by direction:")
print(summary(as.factor(result$data$Direction)))

```
One factor to consider in the analysis of the data is that the reader for a hive wasn't always working.

```{r obsByDate}
temp <- result$data %>% mutate(Hive = as.factor(HexAddress)) %>%
  group_by(FlightDate, Hive) %>% select(FlightDate, Hive) %>%
  summarize(Count = n())
earliest11 <- min(temp %>% filter(Hive == 11) %>% pull(FlightDate))
latest11 <- max(temp %>% filter(Hive == 11) %>% pull(FlightDate))
ggplot(temp, aes(fill = Hive, y = Count, x = FlightDate)) + 
  geom_bar(position = "stack", stat = "identity") +
  labs(title = "Observations by Date by Hive", x = "Date", y = "# Observations")
print(paste("Earliest Date of Observations for Hive 11:", earliest11))
print(paste("Lastest Date of Observations for Hive 11:", latest11))
ggplot(temp %>% filter(FlightDate >= earliest11 & FlightDate <= latest11), aes(fill = Hive, y = Count, x = FlightDate)) + 
  geom_bar(position = "stack", stat = "identity") +
  labs(title = paste("Observations by Date by Hive from", earliest11, "through", latest11), 
       x = "Date", y = "# Observations")
```

Concerns this creates:
Distorts measures of drift (movement between hives)
Distorts # of flights per bee
Distorts # flights by age
How to address?  Focus on good reader Hive 10?

**Flights**    Flights are defined/measured based on a departure observation followed by an arrival
observation for the same bee on the same day.  
```{r flights1}
flights <- result$flights %>% mutate(DepHive = as.factor(DepHive), 
                                     ArrHive = as.factor(ArrHive),
                                     Duration = as.numeric(Duration)/60)
print(paste("# Flights:", nrow(flights)))
print(paste("# of observations used in these flight (2 x nFlights):", 2 * nrow(flights)))
print(paste0("% of observations used in these flight: ", 
             round(100 * 2 * nrow(flights) / result$nObs, 0), "%"))
print(paste("# Bees with flights:", length(unique(flights$TAG))))
```


## How many flights does a bee take
The following are different ways of looking at the number of flights bees took.
```{r FlightsPerBee}
temp <- flights %>% group_by(TAG) %>% summarise(Count = n())
print(summary(temp$Count))
ggplot2::qplot(temp$Count, bins = 30) + xlab("Number of Flights Taken") +
  ylab("Number of Bees Taking Number of Flights on Horizontal Axis") +
  labs(title = "Frequency of Number of Flights Taken")
ggplot(temp, aes(x = "All Bees", y = Count)) + geom_boxplot() + ylab("Number of Flights") +
  xlab("") + labs(title = "Boxplot of Number of Flights By a Drone")
```
```{r FlightsByBee}
ggplot(flights %>% mutate(Duration = pmin(as.numeric(Duration), 60)), aes(x = Departure, y = TAG)) + 
  geom_point(aes(colour = DepHive, size = Duration), shape = 16, alpha = .5) +
  xlab("Departure Date") + labs(title = "Fight Date and Duration by Drone")
```

## How long (duration) are the flights?
```{r flightDuration}
print("Duration of flights in minutes")
print(summary(as.numeric(flights$Duration)))

ggplot(flights, aes(x = "All Bees", y = Duration)) + geom_boxplot() + ylab("Number of Flights") +
  xlab("Duration (mins)") + labs(title = "Boxplot of Duration of Flights")

ggplot2::qplot(flights %>% filter(Duration <= 120) %>% pull(Duration), bins = 30) + xlab("Duration of Flights") +
  ylab("Number of Flights by Flight Duration") +
  labs(title = "Frequency By Flight Duration (max 120 minutes)")

ggplot(flights %>% filter(Duration <= 125), aes(x = as.numeric(Age), y = Duration)) + geom_point() +
  ylim(0, 125) + xlab("Age of Drone") + ylab("Duration of Flight (scale limited to 125)") +
  labs(title = "Duration of Flight by Age of Drone")

```

## When do they fly (time of departure)
The times of departure have been rounded to 15 minute increments.  Per the following chart there 
are a few flights at almost every time of day.  The chart after truncates the times to 9:00 to 20:00.
```{r flightDeparture}
temp <- flights %>% mutate(DepInterval = round_date(Departure, "15 minutes")) %>%
                    mutate(DepInterval = hms::as_hms(DepInterval)) 
temp1 <- temp %>% group_by(DepInterval) %>% summarize(Count = n())
print(summary(temp1$DepInterval))
ggplot(temp1, aes(x = DepInterval, y = Count)) + geom_bar(stat = "identity")
ggplot(temp1 %>% filter(DepInterval >= as_hms("09:00:00") & DepInterval <= as_hms("20:00:00")), aes(x = DepInterval, y = Count)) + 
  geom_bar(stat = "identity")

```
# Weather    
Weather data comes from the [Georgia Tech WeatherSTEM](https://gatech.weatherstem.com) site. We use the
university's Campus Recreaton Center location.  Descriptions of the data items can be found [here](https://gatech.weatherstem.com/data).  We extracted data in 1 minute increments from `r min(weather$Timestamp)` to `r max(weather$Timestamp)`.  Below is a summary of the data.  

```{r weatherSummary}
summary(weather %>% select(-"Record.ID"))
```

```{r joinFlightsWithWeather}
# The following lines convert the Departure to Eastern
temp <- flights %>% mutate(Departure = Departure + hours(4)) %>% 
  mutate(Departure = round_date(Departure, "minute")) %>% 
  select(Departure, Birthday, Age, Duration)
temp$Departure <- with_tz(temp$Departure, "America/New_York")

temp1 <- weather %>% 
  select(Timestamp, X10.Minute.Wind.Gust, Anemometer, Ground.Temperature, 
                            Hygrometer, Rain.Gauge, Thermometer, Wind.Chill)

temp2 <- left_join(temp, temp1, by = c("Departure" = "Timestamp"))
```

